An open source scientific article

### 2021-10-28 src/ms.tex
adding a figure
adding second sigma inference figure
adding a few more figures

\begin{abstract}
	The Early Data Release 3 (EDR3) from the \Gaia\ Mission includes measurements of the radial velocities (RVs) of more than 7 million targets with the goal of providing a detailed view of the phase space of the Milky Way.
	Many of these stars are, in fact, members of unresolved multiple star systems and the effects of these orbits are generally seen as a source of contamination in the RV catalog.
	In this paper, we demonstrate that the published RV error estimates can provide evidence for the existence of an unresolved stellar companion and, under the assumption of a gravitationally-bound binary system, place constraints its orbital parameters.
	This paper makes three key contributions:
	\emph{(1)} We build a flexible data-driven model to estimate \Gaia's intrinsic per-transit RV uncertainty as a function of color and apparent magnitude.
	\emph{(2)} Using these estimates, we develop a procedure for quantifying the likelihood that a given RV target is an unresolved multiple-star system, and compute apply this procedure to all targets with at least 3 RV transits in EDR3.
	\emph{(3)} Finally, we derive a physical model for inferring the orbital parameters of the binary system based only on the published RV error, the number of RV transits, and the observational baseline.
	These parameters are generally only weakly constrained, with the exception of the RV semi-amplitude, which can typically be estimated with a precision of $\sim PPP\%$.
	To demonstrate the reliability of this method and quantify its completeness, we apply our method to simulated data and catalogs of previously known spectroscopic binaries.
	We expect that this value-added catalog will be useful for population studies of binary star systems, target selection for precise RV surveys, vetting exoplanet discoveries, and other applications.
\end{abstract}

@@

For each RV target, the \Gaia\ EDR3 catalog reports the median RV, an estimate of the error on this median, and the number of individual RV measurements (called ``transits'') that were used in this estimate.
In our analysis, we ignore the median RV and instead only consider the RV error and number of transits.
The RV error $\epsilon_n$ for a target $n$ is computed as \citep{Katz19}
\begin{eqnarray}
	{\epsilon_n}^2 = \left(\sqrt{\frac{\pi}{2\,T_n}}\,s_n\right)^2 + 0.11^2
\end{eqnarray}
where
\begin{eqnarray}
	\label{eq:sample-var}
	{s_n}^2 = \frac{1}{N-1}\sum_{t=1}^{T_n} \left(v_{n,t} - \bar{v}_n\right)^2
\end{eqnarray}
is the sample variance of the individual RV measurements $v_{n,t}$.
In \autoref{eq:sample-var}, $t=1,\cdots,T_n$ indexes the $T_n$ transits for target $n$ and
\begin{eqnarray}
	\bar{v}_n = \frac{1}{N}\sum_{t=1}^{T_n} v_{n,t}
\end{eqnarray}
is the mean RV.
In all that follows, it is much simpler to reason about the sample variance ${s_n}^2$ instead of the error on the median ${\epsilon}_n$, but that isn't a problem because we can compute
\begin{eqnarray}
	{s_n}^2 = \frac{2\,T_n}{\pi}\left({\epsilon_n}^2 - 0.11^2\right)
\end{eqnarray}
for any target, using only values available in the catalog: $\epsilon_n$ and $T_n$.

@@

@@

>>>>

\begin{abstract}
	The Early Data Release 3 (EDR3) from the \Gaia\ Mission includes measurements of the radial velocities (RVs) of more than 7 million targets with the goal of providing a detailed view of the phase space of the Milky Way.
	Many of these stars are, in fact, members of unresolved multiple star systems and the effects of these orbits are generally seen as a source of contamination in the RV catalog.
	In this paper, we demonstrate that the published RV error estimates can provide evidence for the existence of an unresolved stellar companion and, under the assumption of a gravitationally-bound binary system, place constraints its orbital parameters.
	This paper makes three key contributions:
	\emph{(1)} We build a flexible data-driven model to estimate \Gaia's intrinsic per-transit RV uncertainty as a function of color and apparent magnitude.
	\emph{(2)} Using these estimates, we develop a procedure for quantifying the likelihood that a given RV target is an unresolved multiple-star system, and compute apply this procedure to all targets with at least 3 RV transits in EDR3.
	\emph{(3)} Finally, we derive a physical model for inferring the orbital parameters of the binary system based only on the published RV error, the number of RV transits, and the observational baseline.
	These parameters are generally only weakly constrained, except for the RV semi-amplitude, which can typically be estimated with a precision of $\sim PPP\%$.
	To demonstrate the reliability of this method and quantify its completeness, we apply our method to simulated data and catalogs of previously known spectroscopic binaries.
	We expect that this value-added catalog will be useful for population studies of binary star systems, target selection for precise RV surveys, vetting exoplanet discoveries, and other applications.
\end{abstract}

@@

For each RV target, the \Gaia\ EDR3 catalog reports the median RV, an estimate of the error on this median, and the number of individual RV measurements (called ``transits'') that were used in this estimate.
In our analysis, we ignore the median RV and instead only consider the RV error and number of transits.
The RV error $\epsilon_n$ for a target $n$ is computed as \citep{Katz19}
\begin{eqnarray}
	{\epsilon_n}^2 = \left(\sqrt{\frac{\pi}{2\,T_n}}\,s_n\right)^2 + 0.11^2
\end{eqnarray}
where
\begin{eqnarray}
	\label{eq:sample-var}
	{s_n}^2 = \frac{1}{T_n-1}\sum_{t=1}^{T_n} \left(v_{n,t} - \bar{v}_n\right)^2
\end{eqnarray}
is the sample variance of the individual RV measurements $v_{n,t}$.
In \autoref{eq:sample-var}, $t=1,\cdots,T_n$ indexes the $T_n$ transits for target $n$ and
\begin{eqnarray}
	\bar{v}_n = \frac{1}{T_n}\sum_{t=1}^{T_n} v_{n,t}
\end{eqnarray}
is the mean RV.
In all that follows, it is much simpler to reason about the sample variance ${s_n}^2$ instead of the error on the median ${\epsilon}_n$, but that isn't a problem because we can compute
\begin{eqnarray}
	{s_n}^2 = \frac{2\,T_n}{\pi}\left({\epsilon_n}^2 - 0.11^2\right)
\end{eqnarray}
for any target, using only values available in the catalog: $\epsilon_n$ and $T_n$.

Now, for a given target $n$, in the absence of any excess radial velocity signal, and if we know it's per-transit radial velocity measurement uncertainty $\sigma_n$, we would expect the quantity
\begin{eqnarray}
	\frac{(T_n - 1)\,s_n^2}{{\sigma_n}^2}
\end{eqnarray}
to be chi-squared distributed with $T_n - 1$ degrees of freedom.

@@

\begin{figure}
	\begin{centering}
		\includegraphics{figures/infer_sigma_data.pdf}
		\caption{A figure.}
		\label{fig:infer_sigma:data}
	\end{centering}
\end{figure}

\begin{figure}
	\begin{centering}
		\includegraphics{figures/infer_sigma.pdf}
		\caption{A figure.}
		\label{fig:infer_sigma:results}
	\end{centering}
\end{figure}

@@

\begin{figure}
	\begin{centering}
		\includegraphics{figures/noise_model.pdf}
		\caption{A figure.}
		\label{fig:noise_model}
	\end{centering}
\end{figure}

\begin{figure}
	\begin{centering}
		\includegraphics{figures/sigma_cmd.pdf}
		\caption{A figure.}
		\label{fig:sigma_cmd}
	\end{centering}
\end{figure}

\begin{figure}
	\begin{centering}
		\includegraphics{figures/binary_fraction_cmd.pdf}
		\caption{A figure.}
		\label{fig:binary_fraction_cmd}
	\end{centering}
\end{figure}

\begin{figure}
	\begin{centering}
		\includegraphics{figures/completeness.pdf}
		\caption{A figure.}
		\label{fig:completeness}
	\end{centering}
\end{figure}
